{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-07-28 swmp_noise.tex
correlation of metab with mean tidal derivative by metabolic period works

% example of detiding a simulated time series
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

{\centering \includegraphics[width=\maxwidth]{figure/do_dtd}

\caption[Example of detiding a simulated \ac{DO} time series]{Example of detiding a simulated \ac{DO} time series.  Simulated values are those in \cref{fig:do_sim}.  Yellow indicates daylight periods.\label{fig:do_dtd}}
\end{figure}

@@

% example from SAPDC
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

@@

% example from ELKVM
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

@@

% example from pdbby
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

>>>>

% example of detiding a simulated time series
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: could not find function "{}wtreg\_fun"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'prd\_tmp' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'prd\_tmp' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: it is only valid to get a child from a "{}gTree"{}}}\end{kframe}
\end{knitrout}
\vfill
\clearpage

@@

% example from SAPDC
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'inst\_subs\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'names' attribute [1] must be the same length as the vector [0]}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'dat.in\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'dat.in\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo3' not found}}\end{kframe}\begin{figure}[!ht]

@@

% example from ELKVM
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'inst\_subs\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'names' attribute [1] must be the same length as the vector [0]}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'dat.in\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'dat.in\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo3' not found}}\end{kframe}\begin{figure}[!ht]

@@

% example from pdbby
\centering\vspace*{\fill}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'inst\_subs\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: 'names' attribute [1] must be the same length as the vector [0]}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo1' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'dat.in\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: do not know how to convert 'dat.in\$DateTimeStamp' to class "{}Date"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo2' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: object 'to\_plo3' not found}}\end{kframe}\begin{figure}[!ht]
